Algebraic File Synchronization: Adequacy and Completeness

### 2017-10-20 p2/works-inverse.tex
Extending domains to canonical sequences

By definiton,
for any filesystem $\FS$ and command $\alpha$, 
$\T{\alpha}(\T{\FS}) = \T{(\alpha\aFS)}$.

Also, for all objects where it is defined, $\T{a}\typeeq a$.
As canonical filesystems, commands, sequences, etc.
are subsets of their non-canonical counterparts, 
all propositions proven so far apply to them as well.
-- TODO NEEDED? % TODO

As the types of values determine whether a command breaks a filesystem,
we know $\Dom{A}=\Dom{\TA}$ and therefore $\Dom{\sqs{A}}=\Dom{\T{\sqs{A}}}$.
TODO FIND A BETTER WAY OF SAYING THIS -- $\Dom{}$ PRESUPPOSES A SET OF % TODO
ALL FILESYSTEMS THAT IS DIFFERENT FOR CANONICAL OBJECTS.
From this it follows that
\begin{mycor}\mlabel{repr_works_is_same}
\begin{gather*}
\worksmnil{\sqs{A}} \Longleftrightarrow \worksmnil{\T{\sqs{A}}} \\
\worksm{\sqs{A}}{\sqs{B}} \Longleftrightarrow \worksm{\T{\sqs{A}}}{\T{\sqs{B}}}.
\end{gather*}
\end{mycor}

@@

We are now ready to define the inverse of canonical commands $\T{\alpha}$
which allows us to move parts of sequences between the
two sides of $\worksmeqsign$.
This is based on the following observation.

>>>>

By definiton, for any filesystem $\FS$ and command $\alpha$, 
$\T{\alpha}(\T{\FS}) = \T{(\alpha\aFS)}$.
This implies $\T{\FS}\in\Dom{\T{\alpha}} \Leftrightarrow \FS\in\Dom{\alpha}$,
where we interpret $\Dom{\T{\alpha}}$ as the subset of canonical filesystems $\T{\alpha}$ is defined on.
This can be extended to sequences and sets of sequences, that is,
\[ \T{\FS}\in\Dom{\T{\sqs{A}}} \Longleftrightarrow \FS\in\Dom{\sqs{A}}. \]

To illuminate this more, we observe
that $\typeeq$-equivalence classes of filesystems are a \emph{partition} of $\setfs$,
and as whether a command is defined on a filesystem is determined solely by its input type,
domains of commands, sequences and sets are unions of these classes:
they either contain a full equivalence class, or none of the filesystems in it.
In other words, $\FS\in\Dom{\sqs{A}} \Leftrightarrow [\FS] \subset \Dom{\sqs{A}}$.
A domain therefore can be fully desribed by the canonical filesystems it contains.

In particular, the above means:

\begin{myclm}\mlabel{repr_works_is_same}
\begin{gather*}
\worksmnil{\sqs{A}} \Longleftrightarrow \worksmnil{\T{\sqs{A}}} \\
\worksm{\sqs{A}}{\sqs{B}} \Longleftrightarrow \worksm{\T{\sqs{A}}}{\T{\sqs{B}}}.
\end{gather*}
\end{myclm}

Also, as canonical filesystems, commands, sequences, etc.
are subsets of their non-canonical counterparts, 
all propositions proven so far apply to them as well.

@@

\noindent We are now ready to define the inverse of canonical commands $\T{\alpha}$
which allows us to move parts of sequences between the
two sides of $\worksmeqsign$.
This is based on the following observation.
